\documentclass[12pt, a4paper]{article}
\usepackage{geometry}
\usepackage{lua-ul}
\usepackage{graphicx}
\usepackage{color,soul}
\usepackage{enumitem}
\usepackage{defaultpreamble}

\setmainfont{Bely}

\begin{document}

\newgeometry{top=1in}

\titlehead{Beyond Good and Evil}{Nietzsche}

\head{The Problem}

\subhead{Dogma}

Dogma is any belief that is considered to be absolutely true.
Such beliefs leave no possibility of reform and improvement. Dogma
is the opposite of science, which encourages growth and
is evidence-based. Dogma causes \textbf{tension in the soul}, especially
in religion; it suppresses instincts and labels them as 'sinful',
causing shame and guilt. The believer enters an internal fight,
where he tries to balance between his absolute believes and 
his instincts. 

\subhead{Passive Nihilism}

When we cut heroine on an addict, he immediately experiences 
withdraw symptoms. This is what happens when we take religion
from people. They start to experience passive nihilism, because
religion is so rooted in tradition and culture. If we were to 
take religion out of the equation, we must provide an alternative,
something that satisfy the spiritual need of the human soul.

\subhead{Christianity is Platonism for the masses}

Christianity draws a lot from Platonism. For one, Platonism advocated that there is 
two worlds: the imperfect -- our world -- which is just an imitation and preparation of the other world,
and the perfect -- the forms. Similarly, Christianity advocated that
life is temporary and a test for the afterlife. Both views devalue life over the life
after, making the 'other' life as the ultimate goal of existence. Platonism also advocated 
that the body is the prison of the soul and similarly Christianity labels natural instincts 
as sinful. Both views create internal struggle within the person possessing the belief.

\subhead{The Antithesis of values}

Metaphysician\footnote{\, the person that believe in a metaphysical world, e.g. Plato and Christians.}
believed of the dualism of values (good x evil, physical x spiritual). This view simplify the
complexity of values and lead people to deny and oppose the 'evil,' it also sacrifice the truth.


\end{document}

