\documentclass[12pt, a4paper]{article}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{lua-ul}
\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{hyperref}

\setlength\parindent{0pt}

\setmainfont{BemboSTd}
\newfontfamily\fonthead{Codex LT}
\newfontfamily\fontsub{Bely}

%sections
\newcommand{\head}[1]{
  \phantomsection
  \section*{\centering{#1}}
  \addcontentsline{toc}{section}{#1}
}

\newcommand{\subhead}[1]{
  \phantomsection
  \subsection*{\centering{\fontsub{#1}}}\vspace{1em}
  \addcontentsline{toc}{subsection}{#1}
}

\newcommand{\subsubhead}[1]{
  \phantomsection
  \subsubsection*{\fontsub{#1}}
  \addcontentsline{toc}{subsubsection}{#1}
}

\newcommand{\quotehead}[2]{
  \phantomsection
  \subsubsection*{\texorpdfstring{\fontsub{#1}}}
  \addcontentsline{toc}{subsubsection}{#2}
}

\begin{document}

\newgeometry{top=0.8in}

\begin{center}
{\fonthead
\Huge{Doctor Faustus}\\[0.2cm]
\Large{Christopher Marlow}\\[0.2cm]
}
\end{center}

\phantomsection
\subsection*{{\fontsub Faustus}}
\addcontentsline{toc}{subsection}{Faustus}
Was born in Germany in Rhodes town, from a humble origin. He
Studied in Wittenberg university. He was an orphan and was raised by a kinsman.
He mastered four branches of knowledge (theology, medicine, logic, law). 
He realizes that these branches are useless and turns to black magic,
selling his soul to Lucifer in exchange for power and ultimate knowledge for 24 years.
He soon forgets about his noble purposes and follow trivial and physical desires. In the end
he regrets following black magic and tries to repent but it is too late.

\subhead{Identify, comment and give the dramatic value of the
following quotations.}

\quotehead{Quote 1/
These metaphysics of magicians\\
And necromantic books are heavenly;\\
Lines, circles, scenes, letters, and characters;\\
Ay, these are those that Faustus most desires.
}{Quote 1}

These lines are said by Faustus in his soliloquy after he realizes that all branches of knowledge 
are useless. Faustus takes interest in necromantic books, saying that those
books are heavenly which is an irony because they are devilish.

\quotehead{Quote 2/
O Faustus lay that damned book aside\\
And Gaze not on it lest it tempt they soul\\
and heap God’s heavy wrath upon they head\\
Read, read the scriptures: that is blasphemy.
}{Quote 2}

These lines are said by Good Angel after Faustus interests in black magic. Good
Angel warns Faustus to leave necromantic books aside because it corrupts the
soul and that God will punish him for it, and instead he should read the holy book.
Good Angel is an abstract character that represent the good in Faustus.

\quotehead{Quote 3/
Go Forward Faustus, in that famous art\\
Wherein all nature’s treasure is contain’d:\\
Be thou on earth as Jove is in the sky,\\
Lord and commander of these elements
}{Quote 3}

These lines are said by Evil Angel after Faustus gets interested in black magic. Evil
Angel encourages Faustus to take black magic and convinces him with the great
that comes from it, telling him he will become like a God (like Jove, which is a
name for Roman God). Evil Angel is an abstract character that represent the evil in Faustus.

\restoregeometry
\quotehead{Quote 4/
 I’ll have them wall all Germany with brass,\\
And make swift Rhine circle fair Wittenberg;\\
I’ll have them fill the public schools with silk,\\
wherewith the students shall be bravely clad\\
I’ll levy soldiers with the coin they bring,\\
And chase the Prince of Parma from our land
}{Quote 4}

These lines are said by Faustus when he was waiting for Valdes and Cornelius.
Faustus is saying his four noble purposes when he gets his magic powers. First he
will build a wall around Germany to protect it. Second he will make the river Rhine
circle around Wittenberg university. Third he will make the students wear silk in
public schools. Fourth he will make a campaign of military to kick the Prince of
Parma. Though when Faustus got his power he pursued physical desires and trivial
things.

\quotehead{Quote 5/
Both law and physic are for petty wits;\\
Divinity is basest of the three,\\
unpleasant, harsh, contemptible, and vile:\\
’Tis magic, magic that hath ravish’d me
}{Quote 5}

These lines are said by Faustus, when he was talking to Valdes and Cornelius,
Faustus says that both law and physics is useless, and that theology is even more
useless, its magic that interest him and give him delight, the repetition of the
word “magic” mark his definite decision to pursue necromancy.

\quotehead{Quote 6/
I charge thee to return and change thy shape;\\
Thou art too ugly to attend on me:\\
Go and return an old Franciscan friar;\\
That holy shape becomes a devil best
}{Quote 6}

These lines are said by Faustus after he preforms necromancy. Faustus tells
these lines to Mephistophilis at his first appearance. He was too ugly so Faustus
ordered him to change his appearance and take the shape of a priest. This is
symbolic to the fact that some clergymen (priests) are hypocrites (pretending
goodness while they are evil inside).

\quotehead{Quote 7/
That was the cause but yet per accidents:\\
For, when we hear one rack the name of God,\\
Abjure the Scriptures and his Saviour Christ,\\
We fly, in hope to get his glorious soul;\\
Nor will we come, unless he use such means
}{Quote 7}

These lines are said by Mephistophilis when Faustus asked him if he was the one who
conjured him. Mephistophilis answers him that when devils hear someone curse the
name of God and abjure him, they fly to him happily to get his \textit{“glorious soul”}. This
is an irony because the person soul will be damned.

\quotehead{Quote 8/
Why this is hell, nor am I out of it:\\
Think’st thou that I, who saw the face of God,\\
And tasted the eternal joys of heaven,\\
Am not tormented with ten thousands hells,\\
In being depriv’d of everlasting bliss?\\
Oh Faustus, leave these frivolous demands\\
Which strike a terror to my fainting soul!
}{Quote 8}

These lines are said by Mephistophilis to Faustus when Faustus asked him why he
consider himself in hell when he can move freely. Mephistophilis answers him
that when he was an angel once he tasted God’s presence, but he was kicked
out with Satan. He says that being deprived of heaven is worse than hell
and it is more tormenting than ten thousand hells. We can
conclude that every place which is not heaven is hell.

\quotehead{Quote 9/
Of wealth !\\
Why, the signiory of Emden shall be mine.\\
When Mephistophilis shall stand by me\\
What God can hurt thee, Faustus? Thou art safe.\\
Cast no more doubts–come, Mephistophilis
}{Quote 9}

These lines are said by Faustus after he had an inner conflict to leave black
magic. Faustus is convinced by Evil Angel to stay in necromancy, leaving his spirit
and turning to his physical desires. He wants to rule over Emden city, and having
Mephistophilis in his side, he is safe from any God’s harm.

\quotehead{Quote 10/
Then, Faustus stab thine arm courageously\\
And bind thy soul, that at some certain day\\
Great Lucifer may claim it as his own\\
And then be thou as great as Lucifer.
}{Quote 10}

These lines are said by Mephistophilis after Faustus agrees to give his soul to
Lucifer. Mephistophilis tells Faustus that he needs to stab his arm and use the blood
to sign a contract with Lucifer. In this way Faustus soul will be claimed by Lucifer 
in exchange of 24 years of magical powers.

\quotehead{Quote 11/
Within the bowels of these elements,\\
Where we are tortur’d and remain for ever:\\
Hell hath no limits, nor is circumscrib’d\\
in of self place; for where we are is hell\\
And where hell is, there must we ever be:
}{Quote 11}

These lines are said by Mephistophilis when Faustus asked him about hell for the
second time. Mephistophilis says that hell has no limit nor it is circumscribed to
any place. Rather it is a state of being where one is deprived of God’s presence,
and any place that is not heaven is hell.


\quotehead{Quote 12/
But what is this inscription on mine arm?\\
Homo, fuge:whither should i fly?\\
If unto God, he’ll throw me down to hell.\\
My senses are deceiv’d, here’s nothing writ:-\\
I see it plain; here in this place is writ,\\
Homo, fuge: yet shall not Faustus fly.
}{Quote 12}

These lines are said by Faustus after his blood congeals. An indication of the ugliness of his deed and a sign
of bad omen. Faustus sees an inscription on his arm that says “Homo,fuge”
which means flee human. At first he thinks that his eyes are deceiving him, but
then he looks again and sees the inscription clearly. He acknowledges that if he
tries to flee to God, God will throw him in hell. He ignore the bad omen and continue to
sign the contract with his blood. 

\quotehead{Quote 13/
Marriage is but a ceremonial toy,\\
And if thou lov’st me think no more of it.\\
I’ll cull thee out the fairest courtesans,\\
And bring them every morning to thy bed.\\
She whom thine eye shall like, they heart shall have,\\
Were she as chaste as was Penelope,\\
As wise as Saba, or as beautiful\\
As was bright Lucifer before his fall.
}{Quote 13}

These lines are said by Mephistophilis after Faustus commands him
to bring him a wife. Mephistophilis refuses because marriage is sacred, it
is a union blessed by God, and he as a devil does not accept that. Instead of a wife
Mephistophilis tells Faustus that he can bring him any woman his heart desires,
be it Penelope who is a woman from Greek Mythology who was known for her
chastity, or the wise queen Saba, or Lucifer himself when he was an angel.

\quotehead{Quote 14/
Ay, stay, good Faustus, stay thy desperate steps!\\
I see an angel hovers o’er thy head,\\
And, with a vial full of precious grace,\\
Offers to pour the same into thy soul:\\
Then call for mercy, and avoid despair
}{Quote 14}

These lines are said by the old man to Faustus when he was trying to guide
him to repent and save his soul. The old man represent God’s infinite mercy and
a chance for Faustus to redeem his soul.
However Faustus refuses his help and instead tells Mephistophilis to attack him
and summon up Helen of Troy to distract him.

\newpage
\quotehead{Quote 15/
His faith is great, I cannot touch his soul;\\
But what I may afflict his body with\\
I will attempt, which is but little worth.
}{Quote 15}

These lines are said by Mephistophilis to Faustus after Faustus asked him to
revenge the old man who tried to help Faustus and guide him to redeem his soul. Mephistophilis
tells him that he cannot hurt the old man's pure spirit because of his deep faith.
He can only hurt his body which is insignificant. 


\quotehead{Quote 16/
Cut is the branch that might have grown full straight,\\
And burned is Apollo’s laurel-bough,\\
That sometime grew within this learned man.\\
Faustus is gone: regard his hellish fall,\\
Whose fiendful fortune may exhort the wise,\\
Only to wonder at unlawful things,\\
Whose deepness doth entice such forward wits\\
To practise more than heavenly power permits.
}{Quote 16}

The chorus makes the final and closing comment on the fall of Faustus, and the
moral lesson of the play. They say that Faustus tried to go beyond the limitation
of humanity, and as a result he was damned. The chorus reminds the audience to
learn from Faustus and respect the limits of things, and to express the medieval
idea that Faustus fall was a result of his pride and ambition.


\subhead{Comment on the following lines critically.}

\quotehead{Line 1/ O, this cheers my soul!}{Line 1}

Faustus says this line to Valdes and Cornelius after they told him on what black
magic can do. That he no longer need to study anything else and enrich him with
all branches of knowledge. This is a reference to the renaissance and the believe that
humans can do anything and are not confined by the limitation of the middle 
Ages. It is the age of hunger for knowledge.

\quotehead{Line 2/A sound magician is a demigod}{Line 2}

Faustus says this line when he gets interested in black magic, saying that a magician
is like a God, who can do anything. It is a reference to the renaissance and 
the believe that man can achieve anything. This was the turning point of Faustus from
scholar to sorcerer. 

\quotehead{Line 3/O, by aspiring pride and insolence}{Line 3}

Mephistophilis says this line to Faustus about Lucifer. That Lucifer was an angel once
but was kicked from heaven because he did not bow to Adam and Eve when God order him to do so.
His arrogance and insolence caused him to be sent to hell together with the unhappy spirits
(the fallen angels).


\quotehead{Line 4/This word “damnation” terrifies not him}{Line 4}

Faustus says this line to Mephistophilis after he abjures God and the holy book.
Even though Mephistophilis tells him that being deprived of heaven equals a thousands hells,
Faustus does not care and say that he is not afraid to be damned (sent to hell) and willing to
continue to sell his soul to Lucifer.

\quotehead{Line 5/The reward of sin is death; that’s hard}{Line 5}

Faustus says this line when he was discussing the uselessness of all branches of knowledge 
and he arrives at theology. Faustus reads the bible and finds a contradiction, in one place it says the reward
of sin is death, in another that we all sin. Faustus then wonders why would God create us to
go to hell. As a result he abandons theology.

\quotehead{Line 6/The God thou serv’st is thine own apatite}{Line 6}

Faustus says this line after he hears a voice that tells him to abandon black magic
and turn to God. Faustus says that God does not love him, and that the god he
serve is his own desires and pleasures.

\quotehead{Line 7/Had not sweet pleasure conquer’d deep despair}{Line 7}

This line is said by Faustus after having doubt to leave black magic and repent to
God. He realizes that his soul is damned and he starts to think of suicide but his
pleasure beats his despair. He turns to physical desires for relieve from the despair
he is in. Faustus had many chances to repeat but his temptation always wins.

\quotehead{Line 8/I do repent, and yet I do despair}{Line 8}

This line is said by Faustus after the old man tried to help him to repent and save
his soul while he still have time. Faustus has a conflict where one part of him
wants to repent and the other wants to continue following black magic.
He tells the old man that he wants to repent but his despair is too great to 
let him do it. He says this because when we are desperate
the devils are stronger and we are easily drawn to their temptations.


\quotehead{Line 9/ 
But mercy, Faustus, of thy Saviour sweet\\
Whose blood alone must wash away thy guilt.
}{Line 9}

These words are said by the old man when he was trying to guide Faustus into repentance.
He tells him that Christ is merciful and that his blood can wash away his
sins and saves his soul. According to the Christian creed Christ has
sacrificed himself to remove the original sin committed by Adam and Eve
when they ate from the forbidden tree of knowledge.

\newpage
\quotehead{Line 10/
Let Faustus live in hell a thousand years,\\
A hundred thousand, and at last be sav’d
}{Line 10}

These words are said by Faustus during the last hour of his life. He wishes to live a
thousand years in hell and then be purged of his sin instead of living eternally
there. However it is only a wish because Faustus sold his soul to the devil in
exchange of 24 years of magical power.

\quotehead{Line 11/
O,I’ll leap up to my God!–Who pulls me down?\\
Where is it now? ’tis gone: and see where God\\
stretcheth out his arm, and bends his ireful brows
}{Line 11}

These lines are said by Faustus during the last hour of his life. He says that he
will pray to god to forgive him but something holds him down, his sins. Faustus
pleads for one drop of Christ blood, or even half a drop to save his soul, then he
says “O, spare me Lucifer” which causes the anger of God. Despite God’s anger,
God still offers his hand to Faustus for repentance, yet Faustus does not take it
and he is eternally damned in hell.\medbreak


\subhead{General Questions}

\subsubhead{Question 1: Discuss the view that Dr.Faustus represents the man who lived in the
Renaissance?}

The age of renaissance is characterized by man tendency 
to get ultimate knowledge. Faustus had a desire for ultimate knowledge,
he rebelled against the limitations of the medieval knowledge and its
restriction. Faustus sells his soul to the devil in order to get more 
knowledge and to prove that human is great and can achieve anything.

\subsubhead{Question 2: Define the chorus and what does it say about the play in the opening
speech?}

The Chorus are group of people that provides information, give the moral lesson,
and set the scene of the play to the audience. They are usually not part of the
play. In the play they mentions where did Faustus lived and what college did he went
and his branches of knowledge and interest in black magic.
The Chorus appears three times in the play, in the beginning to provide information 
and set the scene to the audience, in the middle to comment on the play,
and in the end to give the moral lesson of the play.

\subsubhead{Question 3: What do good and evil angels stands for?}

They are abstract characters that represent the inner conflict of Faustus, good
angel tries to make him follow the path of God, bad angel tries to make him follow
black magic. This technique was popular in the medieval moral plays. In the play
\textit{Dr.Faustus} there is three types of characters: the good, like Good Angel 
and the Old man, who tries to make Faustus repent and forget about black magic.
The bad, like Evil Angel and Valdes and Cornelius, who tries to temp
Faustus to follow black magic. The neutral, like the chorus, who do not participate 
in the play.


\subsubhead{Question 4: Show how Faustus left all branches of knowledge and decided to follow
black magic. }

In the first scene we see Faustus inside his private room discussing his mastery of
all the branches of knowledge. First he begins with logic, he says that the aim of
logic is to be a good debater, thus it is useless. Secondly he turns to medicine,
he says that the aim of medicine is health, and humans cannot live eternally or
bring back dead people, so he says goodbye to medicine too. Thirdly theology,
in the Bible there is contradiction, because in one place it says that the reward
of sin is death, and in another it says that everyone will sin, so Faustus abandon
the Bible too. Fourthly law, he say it is useless as well, and after that he chooses
black magic.



\subsubhead{Question 5: What was Mephistophilis first description of hell and give its dramatic
value?}

After Faustus asks Mephistophilis about hell he tells him about Lucifer,
how he was a favorite angel to God once but because of his pride and
insolence he was dismissed from heaven and had become eternally damned in
hell with the fallen angels. Mephistophilis says that being deprived of Gods 
presence is more tormenting than thousand hells.


\subsubhead{Question 6: What was Mephistophilis second description of hell and give its dramatic
value?}

When Faustus asked Mephistophilis about hell for the second time, he
describe to him hell telling him that hell has no limits nor it is circumscribed to
any place rather it is a state of being, which you experience when you are deprived
of the presence of God, and that any place except heaven is hell.

\subsubhead{Question 7: Why did Mephistophilis refuse to bring Faustus a wife?}

When Faustus asked Mephistophilis to bring him a wife he refuses, because marriage 
is a sacred vow, it is a union blessed by God, and devils have nothing to do
with God. Mephistophilis instead tells Faustus that he can have any woman he
likes, be it as chaste as Penelope, or as wise as Queen of Sheba, or as beautiful as
Lucifer himself.


\subsubhead{Question 8: Show the dramatic significance of the court of the duke of Vanhol.}

At the court of duke Vanholt, Faustus asks the duchess if she desires any kind of
food, and she request a dish of ripe grapes. Although it is January, Mephistophilis
goes and returns with a dish, the duke wonders how this is possible. Faustus
explain to him that he has sent Mephistophilis to India. The duchess says that the grapes are the best she has ever
tasted and The duke promises Faustus that he will reward him greatly for this favor.
This scene shows how Faustus forgot about his noble purposes and pursue physical 
desires and trivial things.

\subsubhead{Question 9: Explain what happened to Faustus in Rome and what is the dramatic
significance of the scene of Faustus with the Pope.}

Faustus makes fun of the pope by snatching his dish and make him look like a
fool. The scene depicts the pope as cruel, proud and power-mad person. This scene may be
viewed as a slap stick comedy, Marlow
intention was to please his protestant audience.
It shows how Faustus forgot about his noble purposes and pursued physical 
desires and trivial things.

\subsubhead{Question 10: Show the dramatic significance of at the court of Emperor Carolus the
fifth.}

The emperor Carolus asks Faustus to raise one of the emperor’s ancestor; Alexander
the great and his Paramour. Faustus tells him he cannot raise their actual
bodies, but spirits that resembles them. The emperor’s knight makes fun of Faustus'
ability and Faustus punishes him by adding a pair of horns on his head but 
the emperor asks Faustus to remove them. After that Mephistophilis enters with the spirits
of Alexander and his Paramour, and the emperor reward Faustus.
This scene shows how Faustus forgot about his noble purposes and pursued physical 
desires and trivial things.


\subsubhead{Question 11: What is the dramatic value of the appearance of Lucifer by himself to
Faustus.}

After Faustus satisfied his physical desires, he experiences great distress and conflict 
as to whether keep following black magic or repent.
He invokes the name of Christ to save his damned soul. That's when Lucifer appears to him 
reminding him that his action 
is a violation of the contract and by mentioning Christ he has done great injury to Lucifer.
Lucifer then displays a show for Faustus of the seven deadly sins to amuse him.


\subsubhead{Question 12: What is the importance of the idea of blood which is mentioned several
times in the play \textit{Dr.Faustus}?}

There is two scenes where blood plays an important role.
First when Mephistophilis asks Faustus to stab his arms
and sign a contract with his blood in order to sell his
soul to Lucifer. Two signs of bad omen appeared as Faustus tried to sign,
the first when his blood congealed,
the second was when an inscription appeared on Faustus's arm 
reading "Homo Fuge" which means "fly human". The second scene 
was when Faustus begs for the blood of Christ, wishing he can
get a drop, or half a drop so that he is saved. 
The blood which is used to sign the
contract with the devil is contrasted with the holy
blood of Christ.

\subsubhead{Question 13: What is the dramatic value of the appearance of the old man?}

The old man is Faustus foil, he is physically ugly but has a pure soul. Whereas
Faustus is beautiful but has an ugly soul. The old man serve as God’s messenger to
guide Faustus into repentance and to show Faustus inner conflict.
He refers to Christ blood which contrast the blood
that Faustus made a contract with. Through the contrast between the hero and the 
foil we can see the weaknesses of the hero.

\subsubhead{Question 14: What are the seven deadly sins, mention some of what each of them says
about itself? }


To divert Faustus attention from thinking of repentance, Lucifer order a show of
the seven deadly sins where they appear in front of him and talk about themselves.
First appears \textbf{Pride}, he says “I hate my parents and i can creep everywhere
and that i won’t say anything more unless the room is perfumed”. Second appears
\textbf{Covetousness}, he says ” I wish the house and all people turn into gold”. 
Third appears \textbf{Wrath} , he says “I have nether a father or a mother and i leapt from a lion’s
mouth when it was half an hour years old and from that time it carries its dagger
in its hands and if it does not find someone to fight with it will fight with itself".
Fourth appears \textbf{Envy}, he says ”I cannot read therefore i wish all books to be burnt, and
when i see people eat i wish that a famine hits people”. Fifth appears \textbf{Gluttony}, he says
“My parents left me nothing to eat but only 30 meals a day”. Sixth appears \textbf{Sloth}, he
says “I was born on a sunny beach and i remind there, and i blame Faustus for
ever waking me up”. Seventh appears \textbf{Lechery} he says ” the first letter of my name is L”.
When Faustus saw the show he says \textit{“O, this feeds my soul”} symbolizing his
hunger for knowledge.\medbreak

\textbf{Short answer:}\smallbreak

Lucifer displays a show of the seven deadly sins to divert Faustus attention from
thinking of repentance and to amuse him, it serve as a comic relieve for the
audience. The seven deadly sins are (Pride, Covetousness, Wrath, Envy, Gluttony,
Sloth and Lechery), each sin appear in front of Faustus and describe itself. After
Faustus sees the show he says \textit{“O,this feeds my soul”} symbolizing his hunger for
knowledge.


\subsubhead{Question 15: Discuss the last hour in Faustus life.}

In the last hour of his life Faustus has a monologue with himself where he wishes
that time would stop so that he can save his soul. He wishes one drop of Christ
blood or even half a drop to save his soul. He wishes that the hills and mountains
would fall on him to hide him from God’s anger. When the clock strikes for half
past the hour, he wishes that god will shorten his time in hell for a thousand year,
or a hundred thousand years but he knows that hell is eternal. He wishes that
the reincarnation is real and that he will be an animal instead of going to hell. He
curses his parents, then himself, and finally Lucifer. When the clock strikes midnight 
and thunder and lighting scaring the skies, he cries aloud for his soul to dissolve 
into the air so that the devil cannot find it, when the devils enter Faustus begs 
God and the devil for mercy, but the devils
drags him away. This is one of the most dramatic moment in the play, where Faustus tries to find a
way out to redeem his soul but he finds no escape. This scene raises the question
of why Faustus last cries to Christ for mercy are not heard, in a truly Christian
framework Faustus would be forgiven even at the last moment, but Marlowe’s
play proves more tragic than Christian, and so there comes a point where he is
no longer can be saved, in other words he was damned while he was still alive.\medbreak

\textbf{Short Answer:}\smallbreak

In the last hour of his life Faustus wishes that if time could stop so that he can
save his soul, and that may God throw him in hell for a thousand or hundred
thousand years but not eternally. He wishes that the mountains could fall on him to
hide him from God’s anger.
In the last moments he begs God and Christ to save him but they do not hear
him and the devils take him away. This scene shows Marlowe’s play to be more
tragic than Christian, because in Christianity you would be forgiven even in the
last moment.\bigbreak

\subhead{Give very short answers to the following questions.}

\subsubhead{Q/ What did Faustus asked Mephistophilis to do when the latter appeared to
him for the first time?}

Change his shape to a priest.

 
\subsubhead{Q/ What are the two traits that made Lucifer get kicked from heaven?}

Pride and insolence.
 
\subsubhead{Q/ To which myth the chorus refers to in the beginning of the play?}

Icarus and Daedalus.
 
\subsubhead{Q/ What was Lucifer before the fall?}

A beautiful angel.
 
\subsubhead{Q/ What was Lucifer Condition for Faustus?}

That he never mentions Christ’s name.
 
\subsubhead{Q/ What were the two signs that appeared to Faustus when he was signing
the contract?}

His blood congealed, and an inscription appeared on his arm “Homo,fuge”.
 
\subsubhead{Q/ Why did Mephistophilis refused to bring Faustus a wife?}

Because marriage is a union blessed by God.
 
\subsubhead{Q/ Name four names for Lucifer?}

Satan, Prince of Darkness, Belzebub and The Devil.
 
\subsubhead{Q/ What is the name of the ceremony when Faustus went to Rome?}

Papal inauguration.
 
\subsubhead{Q/ Who made fun of Faustus and what did Faustus do to punish him?}

A knight in the Emperor palace, Faustus punished him by giving him horns.

\subsubhead{Q/ What did Faustus bring to the Duke’s wife and in which time?}

Faustus brought grape to The Duke’s wife in winter.
 
\subsubhead{Q/ Where does the Chorus appears?}

In the beginning, middle and end.
 
\subsubhead{Q/ What are the function of the Chorus? }

Provide information about the play, set the scene to the audience and give the
moral lesson.
 
\subsubhead{Q/ Why did Faustus asked Mephistophilis to change his shape to Franciscan
(a priest)? }

To show the hypocrisy of the clergymen.

\subsubhead{Q/ What does the old man represent?}

Faustus’s foil.

\subsubhead{Q/ Who did Faustus wanted as paramour?}

Helen of Troy.

\subsubhead{Q/ What did the emperor asked Faustus to do?}

To bring back Alexander the Great and his Paramour.

\subsubhead{Q/ What does “Homo,fuge” means?}

Flee human.

\subsubhead{Q/ Why does Mephistophilis refuse to answer Faustus when he asks him
about who made the world?}

Because it would show God’s miracle.

\subsubhead{Q/ What happened to Faustus when he first got his power?}

He became young and handsome.

\subsubhead{Q/ Why does Lucifer wants to have Faustus soul?}

To enlarge his kingdom.

\subsubhead{Q/ What are the reasons that makes devils appear to humans?}

Abjure and curse God and Christ.

\subsubhead{Q/ Who was with Faustus in the last hour of his life?}

His Colleagues (Three Scholars).

\subsubhead{Q/ Marlowe’s play, Doctor Faustus, reflects the debate of Renaissance theologians
over what opposing ideas?}

Fate versus free will.
 
\subsubhead{Q/ When he first summons Mephastophilis, how does Faustus ask him to
appear?}

In the shape of Franciscan Friar.
 
\subsubhead{Q/ In the last scene of the play ,The Blood of Christ disappeared from the sky
because?}

Because Faustus invoked Lucifer to spare him.
 
\subsubhead{Q/ What is the common thing that Lucifer, Faustus and Icarus share?}

Pride.
 
\subsubhead{Q/ What trick does Faustus, while invisible, play on the pope?}

He steals dishes of food and disrupts the pope’s banquet.
 
\subsubhead{Q/ What is the significance of the line, “Why, this is hell, nor am I out of it”?}

It reflects Mephistophilis’ regret over losing his soul.
 
\subsubhead{Q/ The old man asked Faustus to?}

Forget about suicide.

\subsubhead{Q/ According to the Christian creed, Christ sacrificed himself when crucified
in order to?}

To remove the original sin from human being.

\subsubhead{Q/ According to Mephistophilis “hell” is simply?}

The deprivation of the presence of God.
 
\subsubhead{Q/ How many years was Faustus promised with black magic?}

24 years.
 
\subsubhead{Q/ Why did Faustus sold his soul to the devil?}

Because of his hunger for knowledge.
 
\subsubhead{Q/ What did Faustus do with his power?}

He pursued physical desires and trivial things.
 
\subsubhead{Q/  What does Mephistophilis do when Faustus want to repent?}

He distract him with physical pleasures.

\subsubhead{Q/ Who is Jove which is mentioned by the Evil Angel?}

A name for God.
 
\end{document}
