\documentclass[12pt, a4paper]{article}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{lua-ul}
\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{hyperref}

\geometry{top=1in, bottom=1in}
\setlength\parindent{0pt}

\setmainfont{Alegreya}
\newfontfamily\fonthead{LobsterTwo}

\setotherlanguage{arabic}
\newfontfamily\arabicfont[Script=Arabic, Scale=1]{Amiri}

%sections
\newcommand{\head}[1]{
  \phantomsection
  \section*{\centering{\fonthead{#1}}}
  \addcontentsline{toc}{section}{#1}
}

\newcommand{\subhead}[1]{
  \phantomsection
  \subsection*{\centering{\fonthead{\Large{#1}}}}
  \addcontentsline{toc}{subsection}{#1}
}

\newcommand{\subsubhead}[1]{
  \phantomsection
  \subsubsection*{#1}
  \addcontentsline{toc}{subsubsection}{#1}
}

\begin{document}

\newgeometry{top=0.5in,bottom=1in}

\begin{center}
{\fonthead
\Huge{\textbf{Twelfth Night}}\\[0.2cm]
\Large{Shakespeare}
}
\end{center}

\subhead{Identify, comment and give the dramatic
value of the following extract.}\bigbreak

\subsubhead{\texorpdfstring{Quote 13/
But oh, how vile an idol proves this god!\\
Thou hast, Sebastian, done good feature shame.\\
In nature there's no blemish but the mind.\\
None can be called deformed but the unkind.\\
Virtue is beauty, but the beauteous evil\\
Are empty trunks o'erflourished by the devil.}{Quote 13}
}

These lines are said by The Second captain Antonio who 
saved Sebastian from the Shipwreck. Antonio proves to 
be loyal and devoted to Sebastian by providing him with 
funds, caring for him and even defending him in a 
duel. He mistook Cesario as Sebastian . Believing that his 
young friend is denying him, Antonio is deeply wounded. 
At this point; he speaks bitterly of love's betrayal and 
ingratitude. Antonio says that he was adoring Sebastian 
like a god but this god proved to be an idol that does not 
deserve love nor kindness. He adds that 
sometimes appearances are misleading and that deformity 
lies in the qualities of people 
and not in their bodies. Virtue is always beautiful but evil 
sometimes disguise itself with beauty. He then compares 
ungrateful people to empty and hollow trunks that are 
flourished by the devil.

\subsubhead{\texorpdfstring{quote 14/
a blank, my lord. she never told her love,\\
but let concealinent, like a worm it the bud,\\
feed on her damask cheek. she pined in thought.\\
and with a green and yellow melancholy\\
she sat like patience on a monument,\\
smiling at grief. was not this love indeed?\\
we men may say more, swear more, but indeed\\
our shows are more than will, for still we prove\\
much in our vows, but little in our love}{quote 14}
}

These lines are said by Cesario (Viola) as an answer to Orsino's 
argument that men's love are greater than women's love .
She tells him about her sister, who secretly loved a man but never 
confessed her feelings. She kept that love inside until it destroyed 
her beauty and made her complexion turn yellow and the redness of 
her cheek fade away. Cesario say that men give vows and promises but
sometimes without actions. That their love is mere words and it is not
sincere. Whereas women can love for years without saying a word.

\restoregeometry

\subsubhead{\texorpdfstring{Quote 15/
“This fellow is wise enough to play the fool;\\
And to do that well craves a kind of wit:\\
He must observe their mood on whom he jests,\\
The quality of persons, and the time,\\
And, like the haggard, check at every feather\\
That comes before his eye. This is a practise\\
As full of labouras a wise man's art\\
For folly that he wisely shows is fit; \\
But wise men, folly-fallin, quite taint their wit.“}{Quote 15}
}

These lines are said by Cesario (Viola) about Feste 
when she had a conversation with him at Olivia's gate.
Feste is a wise fool because he sees through people's lies and
stupidity. He uses his wit and wisdom to revel the truth to other 
characters. When Viola asked him if he is Olivia's fool, he tells 
her that he is no fool. And that his role is to undermine the 
stupidity of his Lady and show her the truth.

\subhead{General Questions}\bigbreak

\subsubhead{Q4/ Trace what has happened to Sebastian in
the play.}

Sebastian was saved by Antonio from shipwreck. After that Antonio took
care of him in his own home. At first Sebastian give him a false name,
but after he trusts him, he tells him his true identity and the tale of
his sister, who he assumes to be drowned in the shipwreck. Sebastian
then decided to travel to Illyria to explore it. Antonio cannot go
with him because he has a dispute with Duke Orisno. Out of care and
admiration he gives Sebastian a purse full of money. However, after 
Sebastian leave, Antonio decided to risk himself and follow him. When
Antonio arrive at Illyria he sees Cesario (Viola) dueling with Sir Andrew.
He mistakes him for Sebastian and defends him. Later on Sir Andrew 
sees Sebastian (mistaken him for Cesario) and defies him, but he gets
defeated by Sebastian. When Olivia encounter Sebastian she thinks 
he is Cesario and asks him to marry her. Sebastian is surprised 
since he never have seen her before. However, he sees that she is 
wealthy and beautiful so he accept her proposal. In the end of the
play the two twins are reunited and all complication gets resolved.
The Duke marries Viola and Olivia marries Sebastian and Malvolio
gets release from prison.

\subsubhead{Q5/ The Second captain whose name is
Antonio plays an important role in the plot of Twelfth Night. Discuss.
}
Antonio is the caption who saved Sebastian from shipwreck and took
care of him in his own home. At first Sebastian gave him a false name,
but later he reveled his true identity. When Sebastian wanted to go
to Illyria, Antonio gave him a purse to buy some stuff. Antonio
couldn't go with him because of his problems with Orsino. After that
Antonio decides to follow Sebastian and meets Cesario (Viola) 
when he was about to duel. He mistakes him for Sebastian and defends him.
He then asks him for his purse back but Cesario
deny ever taken it or knowing the caption. Antonio feels betrayed and 
heartbroken. He accuses Cesario of being ungrateful and that he does not deserve 
his devotion. After that Orsino's men
arrest him and he is put in prison. However, the play ends happily and 
Antonio is released from prison.

\subsubhead{Q6/ Who is Malvolio and what was Maria, Feste Sir 
Toby and others' plan to revenge from him?}

Malvolio is Olivia's chief servant, a job he takes very seriously.
He is proud and egoistic.
He always gives bad reports about Sir Toby and Sir Andrew
and both Maria and Feste hates him. They decide to revenge him by 
writing a fake letter which Maria wrote imitating the hand writing
of Olivia. The letter hints that Olivia is in love with Malvolio
and that he needs to wear yellow stockings and cross garters 
and smile all the time to proof that he loves Olivia. He swallows
the bait and Olivia thinks he is mad and detain him.

\subsubhead{Q7/ The role played by Maria in
Twelfth Night.}

Maria is the witty and cunning maid of Olivia. She is admired by Sir
Toby. Maria wrote the fake letter and gave it Malvolio to make 
a fool of him. She then tells Olivia that Malvolio is possessed and
that she should be careful with him. She also tells Feste to disguise as
Sir Topas (priest) and go to Malvolio in his prison.

\subsubhead{Q8/ Discuss the theme of disguise and 
mistaken identity in William Shakespeare's Twelfth 
Night.}

Many characters in Twelfth Night assume disguises, 
for example Viola, who disguised herself as a male (Cesario)
so that she can work as a servant to Duke Orsino. Malvolio,
who puts on crossed garters and yellow stockings in the hope of 
winning Olivia's affection. And Feste, who dresses up as a priest 
to fool Malvolio when he was detained in a dark room, even though
Malvolio were not able to see him. Also The instances of mistaken 
identity between the two twins. For example when 
Antonio mistakes Viola (Cesario) for Sebastian, Cesario does 
not recognize Antonio and he feels betrayal and heartbroken. Or when 
Viola is mistaken for Sebastian by Sir Andrew and Sir Toby and then
by Olivia, who promptly marries him. However, in the end all 
identities are reveled and the play ends happily.

\subsubhead{Q9/ Discuss the role which is played by Feste 
the clown in Twelfth Night.}

Throughout history, jesters and fools have used their wits 
to pretend stupidity and folly for the sake of
enjoyment and social satire and to earn their living.
Twelfth Night contains one of Shakespeare's wisest fools.
Feste's role is to point out the truths other characters do
not want to hear. For example Olivia, who is mourning over
her dead brother. Feste asks her where is her brother and 
she answers that he is in heaven, he then wonders why 
should you mourn someone who is in heaven. Also when Cesario asks
him if he is the fool of Olivia, he replies that Olivia has no fool
because she is not married. Meaning that every husband is a fool.
He uses \textit{pun} to play on the word "fool"
which means either "idiot" or "clown". 

\newpage

\subhead{Give very short answers to the following questions}\bigbreak

\subsubhead{Q/How does Olivia react when she realizes she married Sebastian instead of Cesario?}

She is confused but accepts it.

\subsubhead{Q/How does Sebastian react to Olivia’s affection?}

He is confused but accepts her love.

\subsubhead{Q/Why is Antonio arrested in Act 3?}

He is a wanted enemy of Orsino's.

\subsubhead{Q/Why does Sir Andrew challenge Cesario to a duel?}

To win Olivia's love.

\subsubhead{Q/Who challenges Cesario to a duel?}

Sir Andrew Aguecheek.

\subsubhead{Q/What does Sir Toby tell Sir Andrew to do to impress Olivia?}

Challenge Cesario in a duel.

\subsubhead{Q/What does Olivia do after meeting Sebastian?}

She asks him to marry her.

%Malvolio

\subsubhead{Q/Give one feature of Malvolio?}

Very proud of himself.

\subsubhead{Q/How does Malvolio react after reading the letter?}

He believes every word and follows its instructions.

\subsubhead{Q/What phrase does the fake letter tell Malvolio to remember?}

\textit{"Be not afraid of greatness"}.

\subsubhead{Q/Who disguises himself as a priest to trick Malvolio?}

Feste.

\subsubhead{Q/How does Malvolio act after reading Maria’s fake letter?}

He dresses in yellow stockings and smiles constantly.

\subsubhead{Q/What is the main purpose of the fake letter written for Malvolio?}

To make Malvolio look foolish and humiliate him.

\subsubhead{Q/How does Maria make the letter look convincing?}

She writes it in Olivia’s handwriting.

\subsubhead{Q/What happens to Malvolio in Act 4 when he did exactly the instructions mentioned in the letter?}

He is locked in a dark room as punishment.

\subsubhead{Q/Who comes up with the idea to trick Malvolio with a fake letter?}

Maria.

\subsubhead{Q/Where was Malvolio kept when Olivia thought that he went mad?}

A dark room.

\subsubhead{Q/How does Olivia react when Malvolio follows the letter’s instructions?}

She is confused and thinks he has gone mad.

\subsubhead{Q/How did Viola knew that her brother Sebastian was alive?}

When the second captain mistakenly calls her Sebastian.

\subsubhead{Q/Who thinks that men's love is greater than women's love?}

Orsino.

\subsubhead{Q/What kind of comedy Twelfth Night is?}

Romantic comedy.

\subsubhead{Q/Who takes care of Sebastian after he is shipwrecked?}

The second captain Antonio.

\subsubhead{Q/Who is "Jove" Which is mentioned in Maria's letter?}

A name for God.

\subsubhead{Q/By whom was Antonio arrested?}

Orsino's men.

\subsubhead{Q/Whom did Duke Orsino marry in the end of the play?}

Viola.

\subsubhead{Q/Who mistakes Sebastian for Cesario and invites him into the palace?}

Olivia.

\subsubhead{Q/What does Orsino decide to do after learning Viola is a woman?}

He asks her to marry him.

\subhead{Fill The Blank}\bigbreak

\begin{itemize}

\item[\ding{113}] The second captain ask Cesario to give him \underLine{a purse} when he was arrested.

\item[\ding{113}] Olivia give \underLine{a jewel} to Cesario (Viola) as a token of love.

\item[\ding{113}] Viola is saved from the duel with Sir Andrew by \underLine{Antonio}.

\item[\ding{113}] Olivia called a \underLine{priest} to arrange a secret \underLine{marriage} with Sebastian.

\item[\ding{113}] Malvolio believes that the phrase “Be not afraid of \underLine{greatness}“ is a message from Olivia.  

\item[\ding{113}] The letter that was written by Maria was composed of \underLine{poetry} and \underLine{prose}.

\item[\ding{113}] Viola says to the second captain that she hates \underLine{ingratitude} the most.

\end{itemize}

\end{document}
