\documentclass[12pt, a4paper]{article}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{xcolor}

\setmainfont{EB Garamond}


\begin{document}


\begin{center}
\huge{\textbf{Music Genres on Mood}}\\[1.2cm]
\end{center}

 Music is one of the most accessible form of art. It is the universal
language that all people can speak. It is meant to express the artist's
emotions and thoughts. It is used everywhere nowadays, whether in our day to day
life, or in media (like films, video games and social media). Its not just a form 
of entertainment, artists and companies make a lot of money out of it. There is 
so many genres of music, each kind has a different effect on our moods and brain.\bigbreak

Jazz music makes us relaxed and tranquilized. It is not just music 
but a culture movement that is started by the African-American people. Jazz itself
has different types, the common one is \textit{blues}. I personally love listening
to jazz when I want to relax and have a quite time.\bigbreak

Hip-hop become really popular the last century. When I listen to hip-hop I feel
like a gangster. Its amazing how music can alter your emotions and expresses
ones that you already feel. Pop is also something that have been popular lately. It is
calm and mostly talk about love. I do listen to it sometimes when I feel sad 
and depressed.\bigbreak

Rock is upbeat and gives you energy. It is very popular music genre especially 
in America in the 1960s. \textit{The Beatles} were one of the most popular band in this
genre. They contributed so much to the genre that in later years most Rock
bands were influenced by them.\bigbreak

Electronic music is my favourite. It can have all of the above, while keeping 
it all interesting and fun. Its truly amazing how few machines can make 'music' and
how few sounds put together can make the most wonderful melodies. There is an elevated
type of Electronic music that is called \textit{'IDM'} short for (intelligent dance music).
It is a magnificent genre that makes dance music more interesting. It was originated 
in the 90s by artists like \textit{Aphex Twin} and \textit{Autechre}.\bigbreak

Overall music is a great way to express your self and emotions. It is also a good
business if you are interested in being an artist. Music can take you to worlds 
you've never been. When you listen to music, you can feel things that you cannot otherwise 
feel. There is billions of music that is waiting for you to explore them and feel them.

\end{document}


