\documentclass[12pt, a4paper]{article}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{xcolor}

\setmainfont{Calendula}
\newfontfamily\fonthead{AlegreyaSC}


\setlength\parindent{0pt}

\newcommand{\head}[1]{
  \section*{\centering{\fonthead{#1}}}
}


\begin{document}


\head{A Conversation About Eid al-Fitr}\vspace{2em}

\textbf{A:} So, did you went somewhere special in this Eid? Or did you stay at home like everyone else?\bigbreak

\textbf{B:} Actually, I went out with my friend in the second day of Eid.\bigbreak

\textbf{A:} Really? You went in Eid? The roads must have been really busy! \bigbreak

\textbf{B:} It wasn't really. The roads were kinda busy but it did not 
brother us. What about you, did you go out in Eid? \bigbreak

\textbf{A:} Of course not, I thought that I would just stick in traffic for two hours, so i 
did not go anywhere. But tell me where did you go? \bigbreak

\textbf{B:} Me and my friend went to a restaurant than we drank coffee. We talked the whole time. 
We were supposed to go out with a group but we ended up to be the only people wanting to go out in Eid. \bigbreak
\textbf{A:} Yeah because there is this misconception about the traffic and how all the places is just crowded with people. 
Tell me what have you two talked about? \bigbreak
\textbf{B:} We talked about different things, I came to see him in new light afterwards. I really love 
these one on one conversations, I should really do more of them. Did you went out after Eid? \bigbreak
\textbf{A:} Not really because after Eid I had exams and was not really in the mood to go anywhere.
But i really enjoyed my alone time, sometimes i just need to be alone for a time. \bigbreak
\textbf{B:} Yes i understand you. Sometimes just doing your routine and hobbies makes you feel better.\bigbreak

\textbf{A:} Absolutely, anyway it was really nice talking to you. I got a bus to catch.\bigbreak

\centerline{[leaves.]}


\end{document}
