\documentclass[12pt, a4paper]{article}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{tipa}
\usepackage{lua-ul}
\usepackage{color,soul}

\geometry{top=0.6in}
\setlength\parindent{0pt}

\setmainfont{Philosopher}
\newfontfamily\fontpar{BespokeSerif}

\begin{document}


\begin{center}
\huge{Phonetics Second Course}\\[0.5cm]
\Large{By: Birdman}\\[1cm]
\end{center}


\section*{\centering{\LARGE{The Syllable}\\[0.6cm]}}

{\fontpar
\textbf{Syllable}: Is a unit consisting of one vowel which may be 
proceeded or followed by one or more consonant. However there is 
one syllable without a vowel called \textbf{syllablic consonant}.\medbreak

Before we understand syllables, we need to understand the 
difference between vowels and consonants. \textbf{Vowels} produce none to 
little obstruction in the air flow. \textbf{Consonants} produce 
complete or partial obstruction in the air flow.\medbreak

We also need to understand the difference between phonetics and phonology.
\textbf{Phonetics} studies the production of the speech sound, (whether
there is obstruction or not). \textbf{Phonology} studies the distribution
of the phonemes in a language. That's why syllables can be divided into
phonetic and phonology.

\section*{Syllable Phonetically}
Consisting of a centre which has little or no obstruction to the 
airflow.\medbreak

So phonetically we divide words by the amount of obstruction they have 
(how many consonant they have) and where they are in a word:


\begin{description}
  \item[1. Minimum syllable:]Is a single vowel in isolation, which has
    the least amount of obstruction:\medbreak

    \centerline{are \textipa{/A:/} \hspace{2cm} err \textipa{/3:/} }

  \item[2. Onset:]One or more consonant proceeding the centre of
    the syllable:\medbreak

    \centerline{bar /ba:/ \hspace{2cm} key /ki:/}

  \item[3. Coda:]One or more consonant comes after the centre of the 
    syllable:\medbreak

    \centerline{am /æm/ \hspace{2cm} ease /i:z/}

  \item[4. Onset and Code:]Syllable that has proceeding and following
    consonant,\\and it has the most obstruction:\medbreak

    \centerline{ran /ræn/ \hspace{2cm} sat /sæt/}
  
\end{description}

\section*{Syllable Phonologically}
Can be described as the possible combinations of English phonemes,
what sounds can occur in the beginning and ending of words.
\textbf{Phonotactics} is the study of the possible phoneme combinations of a language.

\subsection*{Consonant Cluster}
Can be described as two or more consonants that follow each other without 
a vowel in between them.\medbreak

We divide consonant clusters (or sequences) based on their position:\medbreak

\textbf{Initial position}: In initial position a word can start with one,
two or three consonant, \underLine{3 consonant sequence words only start 
with \textbf{/s/}} ex: \underLine{spr}ay , \underline{str}ing.
\hl{There is no words that start with 
4 consonant}.\medbreak 

\textbf{Zero Onset}: When there is no inital consonant in a word ex:
are \textipa{/A:/}.\medbreak

Any vowel can occur in initial position, although \textipa{/U/} is 
rare. As for consonant \underLine{\textipa{/N/ and /3/} do not come
in initial position}.\bigbreak

\textbf{Final Position}: In final position a word can start with one,
two, three or four consonant, for example the word (texts
\textipa{/teksts/}) ends with 4 consonants. \hl{No words ends with 5 consonant}.\medbreak

Most consonants can occur in final position expect for a few, for example
\hl{there is no word that ends with \textbf{h, j, w}}. 
The consonant \underLine{\textbf{/r/} does not come in final position in
rhotic accents (BBC) }, however in non-rhotic accents (American Eglish) 
\textbf{/r/} can occur at the end. As for vowels, 
\underLine{\textipa{(I, e, æ, U, 2, 6)} these vowels does not come at the
end of a syllable}.\medbreak


\textbf{Zero Coda}: When there is no final consonant in a word, ex:
more \textipa{/mO:/}.\medbreak

\textbf{Ambisyllabic}: A term that is used to describe a consonant 
that belong to both syllables. For example the word better and carry 
should be written like this:\medbreak

\centerline{better \textipa{/bet.@/}\hspace{2cm}carry \textipa{/kær.i/}}
\medbreak

}
\end{document}


